A Data-Driven Early Warning System for Mining Accidents

### 2017-03-24 San Antonio/slides/presentation_slides.Rmd
semi-final slides, again
final-isa draft

---
title: "A Data-Driven Early Warning System for Mining Accident"
shorttitle: "Mining Accident Data Analysis"
author: |
  | Yu Luo, Ashutosh Nanda, Shiva Rajgopal, Vinay Ramesh,
  | Venkat Venkatasubramanian, Zhizun Zhang, and Catherine Zhao
shortauthor: "Luo et al."
institute: |
  | Chemical Engineering, Computer Science, and Business School
  | Columbia University
shortinstitute: "Columbia University"
date: "3/27/2017"
output: 
  beamer_presentation:
    keep_tex: false
    incremental: false
    template: rmd_template.tex
    fig_height: 4.75
    # fig_width: 4
    toc: true
    slide_level: 2
    includes:
      in_header: rmd_header.tex
---

@@

\placelogofalse

- Systemic disasters
    - SARS (2003)
    - Northeast Blackout (2003)
    - Subprime Crisis (2008)
    - Deepwater Horizon Oil Spill (2010)
- Emerging systemic risks
    - Climate change
    - Income/wealth inequality
    - Cyber-physical security
    - Technological singularity
- Fast-paced and connected
- Design complex systems
- Analyze systemic risk

@@

- Formed in	1977
- Agency of the United States Department of Labor
- Mission
    - Prevent death, illness, and injury from mining
    - Promote safe and healthful workplaces for U.S. miners
    - Develop and enforce safety and health rules
    - Provide technical, educational, and other types of assistance
- A constantly improving industry in terms of safety

@@

- Plot violation trends prior to Upper Big Branch and Sago disasters

@@

## Unsupervised Clustering

@@

<!-- https://cran.r-project.org/web/packages/markovchain/vignettes/an_introduction_to_markovchain_package.pdf -->
## Markov Chain

@@

<!-- - Causal relationship between accidents and historical data -->
- Summary
    - Two deadliest mine accidents in the last decade: Upper Big Branch & Sago
    - Rich MSHA data that need clean-up
    - Supervised predictive model
    - Unsupervised clustering of risk
- Application
    - "Credit score" for mine safety
    - Regulators, mines, stakeholders
- Future
    - Improve model performance
    - Expand data: OSHA, EPA, etc.
    - Other techniques: artificial neural networks (restricted boltzmann machine), text mining, etc.

>>>>

---
title: "A Data-Driven Early Warning System for Mining Accidents"
shorttitle: "Mining Accident Data Analysis"
author: |
  | Yu Luo, Ashutosh Nanda, Shivaram Rajgopal, Vinay Ramesh,
  | Zhizun Zhang, Catherine Zhao, and Venkat Venkatasubramanian
shortauthor: "Luo et al."
institute: |
  | Chemical Engineering, Computer Science, and Business School
  | Columbia University
shortinstitute: "Columbia University"
date: "3/27/2017"
output: 
  beamer_presentation:
    keep_tex: false
    incremental: false
    template: rmd_template.tex
    fig_height: 4.75
    # fig_width: 4
    toc: true
    slide_level: 2
    includes:
      in_header: rmd_header.tex
---

@@

- Systemic disasters
    - SARS (2003)
    - Northeast Blackout (2003)
    - Subprime Crisis (2008)
    - Deepwater Horizon Oil Spill (2010)
- Emerging systemic risks
    - Climate change
    - Income/wealth inequality
    - Cyber-physical security
    - Technological singularity
- Fast-paced and connected
- Prevent systemic disasters
- Analyze systemic risk: go beyond one-off accidents

@@

- Formed in	1977, agency of the U.S. Department of Labor
- Mission
    - Prevent death, illness, and injury from mining
    - Promote safe and healthful workplaces for U.S. miners
    - Develop and enforce safety and health rules
    - Provide technical, educational, and other types of assistance
- A constantly improving industry in terms of safety

@@

- Plot violation trends prior to disasters

@@

<!-- - Causal relationship between accidents and historical data -->
- Summary
    - Two deadliest mine accidents in the last decade: Upper Big Branch & Sago
    - Rich MSHA data that need clean-up
    - Supervised predictive model
- Application
    - "Credit score" for mine safety
    - Regulators, mines, stakeholders
- Future
    - Improve model performance
    - Unsupervised clustering, neural nets, etc.
    - Expand data: OSHA, EPA, etc.

## Appendix: Unsupervised Clustering

@@

<!-- https://cran.r-project.org/web/packages/markovchain/vignettes/an_introduction_to_markovchain_package.pdf -->
## Appendix: Markov Chain

@@
